---
title: "Amazon S3"
output:
  html_document:
    df_print: paged
---

*Installation*
Latest Stable Version:
```{r}
# On Mac/Linux:
if (Sys.info()["sysname"] == 'Darwin'){
  Sys.setenv(LDFLAGS="-L/usr/local/opt/openssl@1.1/lib",
             CPPFLAGS="-I/usr/local/opt/openssl@1.1/include",
             PKG_CONFIG_PATH="/usr/local/opt/openssl@1.1/lib/pkgconfig",
             LIBRARY_PATH=paste(Sys.getenv("LIBRARY_PATH"),
                                "/usr/local/opt/openssl@1.1/lib",
                                sep=""))
  dir.create(path = Sys.getenv("R_LIBS_USER"), showWarnings = FALSE, recursive = TRUE)
  install.packages("xml2", configure.vars='INCLUDE_DIR=/usr/local/opt/libxml2/include/libxml2 LIB_DIR=/usr/local/opt/libxml2/lib/')
  install.packages('curl', lib = Sys.getenv("R_LIBS_USER"))
  install.packages('httr')
  install.packages("aws.s3", repos = c("cloudyr" = "http://cloudyr.github.io/drat"))
} else { # On Windows
    install.packages("aws.s3", repos = c("cloudyr" = "http://cloudyr.github.io/drat"), INSTALL_opts = "--no-multiarch")
    # if not working use:
    # install.packages("aws.s3", repos = c("cloudyr" = "http://cloudyr.github.io/drat"))
}
```

Set up your R w/ AWS
```{r}
keyfile = list.files(path=".", pattern="accessKeys.csv", full.names=TRUE)
if (identical(keyfile, character(0))){
  stop("ERROR: AWS key file not found")
} 

keyTable <- read.csv(keyfile, header = T) # *accessKeys.csv == the CSV downloaded from AWS containing your Access & Secret keys
AWS_ACCESS_KEY_ID <- as.character(keyTable$Access.key.ID)
AWS_SECRET_ACCESS_KEY <- as.character(keyTable$Secret.access.key)

#activate
Sys.setenv("AWS_ACCESS_KEY_ID" = AWS_ACCESS_KEY_ID,
           "AWS_SECRET_ACCESS_KEY" = AWS_SECRET_ACCESS_KEY,
           "AWS_DEFAULT_REGION" = "eu-west-1") 
```

Have a look at your buckets on AWS:
```{r}
library(aws.s3)
bucketlist()
```

Creating a unique S3 bucket name:
```{r}
my_name <- "ceu-class-zoltan"  # Type in your name here
bucket_name <- paste(c(my_name, "-", sample(c(0:3, letters), size = 3, replace = TRUE)), collapse = "")
print(bucket_name)
```

Now, create the bucket on S3
```{r}
put_bucket(bucket_name)
```

Bucket location:
```{r}
get_location(bucket_name)
```

Creating a sample text file
```{r}
write("This is a simple text file", "my_content.txt")
```

Send the text file to your AWS S3 bucket
```{r}
put_object(file="my_content.txt", bucket = bucket_name)
```
Now you can now see the file on AWS.

Save files from S3 to your computer
```{r}
save_object("my_content.txt", bucket = bucket_name, file = "my_content_s3.txt")
```

Check the file
```{r}
list.files()
```

Display file contents
```{r}
t = read.table("my_content_s3.txt", sep = "\t" )
t
```

Deleting S3 objects:
```{r}
delete_object("my_content.txt", bucket = bucket_name)
```

Deleting buckets
```{r}
delete_bucket(bucket_name)
```

Try to delete it again. You will see an error!
```{r}
delete_bucket(bucket_name)
```





