---
title: "Amazon S3"
output: html_notebook
---

*Installation*
Latest Stable Version:
```{r}
# On Mac/Linux:
#install.packages("aws.s3", repos = c("cloudyr" = "http://cloudyr.github.io/drat"))

# On Windows you may need:
#install.packages("aws.s3", repos = c("cloudyr" = "http://cloudyr.github.io/drat"), INSTALL_opts = "--no-multiarch")
```

Set up your R w/ AWS
```{r}
keyTable <- read.csv("accessKeys.csv", header = T) # accessKeys.csv == the CSV downloaded from AWS containing your Acces & Secret keys
AWS_ACCESS_KEY_ID <- as.character(keyTable$Access.key.ID)
AWS_SECRET_ACCESS_KEY <- as.character(keyTable$Secret.access.key)

#activate
Sys.setenv("AWS_ACCESS_KEY_ID" = AWS_ACCESS_KEY_ID,
           "AWS_SECRET_ACCESS_KEY" = AWS_SECRET_ACCESS_KEY,
           "AWS_DEFAULT_REGION" = "eu-west-1") 
```

Have a look at your buckets on AWS:
```{r}
library(aws.s3)
bucketlist()
```

Creating a unique S3 bucket name:
```{r}
my_name <- "ceu-class-zoltan"  # Type in your name here
bucket_name <- paste(c(my_name, "-", sample(c(0:3, letters), size = 3, replace = TRUE)), collapse = "")
print(bucket_name)
```

Now, create the bucket on S3
```{r}
put_bucket(bucket_name)
```

Bucket location:
```{r}
get_location(bucket_name)
```

Creating a sample text file
```{r}
write("This is a simple text file", "my_content.txt")
```

Send the text file to your AWS S3 bucket
```{r}
put_object("my_content.txt", bucket = bucket_name)
```
Now you can now see the file on AWS.

Save files from S3 to your computer
```{r}
save_object("my_content.txt", bucket = bucket_name, file = "my_content_s3.txt")
```

Check the file
```{r}
list.files()
```

Display file contents
```{r}
t = read.table("my_content_s3.txt", sep = "\t" )
t
```

Deleting S3 objects:
```{r}
delete_object("my_content.txt", bucket = bucket_name)
```

Deleting buckets
```{r}
delete_bucket(bucket_name)
```

Try to delete it again!
```{r}
delete_bucket(bucket_name)
```





