---
title: "Web Scraping with R"
output:
  html_document:
    df_print: paged
  html_notebook: default
  pdf_document: default
---

```{r}
#Have your SelectorGadget on Google Chrome: https://selectorgadget.com/

#Loading the rvest package
#install.packages("xml2", "rvest")

#Loading the rvest package
library(rvest)

# Specifying the URL 
url <- 'https://www.imdb.com/title/tt0111161/?ref_=adv_li_tt'

#Reading the HTML code from the website
webpage <- read_html(url)

#Using CSS selectors to scrape the rankings section
description_html <- html_nodes(webpage,'#titleStoryLine p span')

#Converting the ranking data to text
description <- html_text(description_html)

print(description)
```

##Optional: Build a dataframe from top-rated movies
```{r}
#Specifying the URL 
url <- 'https://www.imdb.com/search/title/?count=100&release_date=1994,1994&title_type=feature'

#Reading the HTML code from the website
webpage <- read_html(url)

```

*STEP 1:* Let's scrape the Rank field of the movies on IMDB. For that, we’ll use the selector Google Chrome extension gadget.
```{r}
#Using CSS selectors to scrape the rankings section
rank_data_html <- html_nodes(webpage,'.text-primary')

#Converting the ranking data to text
rank_data <- html_text(rank_data_html)

#Data-Preprocessing: Converting rankings to numerical
rank_data<-as.numeric(rank_data)

#Let's have a look at the rankings
head(rank_data)

```

*STEP 2:* Title field
```{r}
#Using CSS selectors to scrape the title section
title_data_html <- html_nodes(webpage,'.lister-item-header a')

#Converting the title data to text
title_data <- html_text(title_data_html)

#Let's have a look at the title
head(title_data)

```

*Step 3:* Description field
```{r}
#Using CSS selectors to scrape the description section
description_data_html <- html_nodes(webpage,'.ratings-bar+ .text-muted')

#Converting the description data to text
description_data <- html_text(description_data_html)

#Data-Preprocessing: removing '\n'
description_data<-gsub("\n","",description_data)

#Let's have a look at the description data
head(description_data)

```

*Step 4:* Runtime field
```{r}
#Using CSS selectors to scrape the Movie runtime section
runtime_data_html <- html_nodes(webpage,'.text-muted .runtime')

#Converting the runtime data to text
runtime_data <- html_text(runtime_data_html)

#Data-Preprocessing: removing mins and converting it to numerical

runtime_data<-gsub(" min","",runtime_data)
runtime_data<-as.numeric(runtime_data)

#Let's have a look at the runtime
head(runtime_data)

```

*Step 5:* Genre field
```{r}
#Using CSS selectors to scrape the Movie genre section
genre_data_html <- html_nodes(webpage,'.genre')

#Converting the genre data to text
genre_data <- html_text(genre_data_html)

#Data-Preprocessing: removing \n
genre_data<-gsub("\n","",genre_data)

#Data-Preprocessing: removing excess spaces
genre_data<-gsub(" ","",genre_data)

#taking only the first genre of each movie
genre_data<-gsub(",.*","",genre_data)

#Convering each genre from text to factor
genre_data<-as.factor(genre_data)

#Let's have another look at the genre data
head(genre_data)

```

*Step 6:* Ratings field
```{r}
#Using CSS selectors to scrape the IMDB rating section
rating_data_html <- html_nodes(webpage,'.ratings-imdb-rating strong')

#Converting the ratings data to text
rating_data <- html_text(rating_data_html)

#Data-Preprocessing: converting ratings to numerical
rating_data<-as.numeric(rating_data)

#Let's have another look at the ratings data
head(rating_data)

#Let's have a look at the ratings
head(rating_data)
```

*Step 7:* Director field
```{r}
#Using CSS selectors to scrape the directors section
directors_data_html <- html_nodes(webpage,'.text-muted+ p a:nth-child(1)')

#Converting the directors data to text
directors_data <- html_text(directors_data_html)

#Data-Preprocessing: converting directors data into factors
directors_data<-as.factor(directors_data)

#Let's have a look at the directors data
head(directors_data)
```

*Step 8:* Actors field
```{r}
#Using CSS selectors to scrape the actors section
actors_data_html <- html_nodes(webpage,'.lister-item-content .ghost+ a')

#Converting the gross actors data to text
actors_data <- html_text(actors_data_html)

#Data-Preprocessing: converting actors data into factors
actors_data<-as.factor(actors_data)

#Let's have a look at the actors data
head(actors_data)
```

*Step 9:* Now we have successfully scraped all the features for the 100 most popular feature films released in 1994. Let’s combine them to create a dataframe and inspect its structure.
```{r}
#Combining all the lists to form a data frame
movies_df<-data.frame(Rank = rank_data, Title = title_data,
                      Description = description_data, Runtime = runtime_data,
                      Genre = genre_data, Rating = rating_data,
                      Director = directors_data, 
                      Actor = actors_data)

#Structure of the data frame
movies_df
```

*Let's plot this*
```{r}
library('ggplot2')

qplot(data = movies_df, Genre,)
```






